Using an iterated block particle filter via \pkg{spatPomp}

### 2023-05-01 ms.Rnw
code updated for pomp 5

<<bm_logLik_eval,cache=F,echo=F,eval=T>>=
bm_dir <- paste0("bm_",i,"/")
if(!dir.exists(bm_dir)) dir.create(bm_dir)
stew(file=paste0(bm_dir,"logLik.rda"),seed=10,{
<<bm_logLik_code>>
  bpf_logLik1 <- replicate(10,
    logLik(bpfilter(b,switch(i,10,1000),block_size=1))
  )
  bpf_logLik4 <- replicate(10,
    logLik(bpfilter(b,switch(i,10,1000),block_size=4))
  )
})
@

@@

<<ibpf-mle-code,eval=F,echo=T>>=
rho_start <- seq(from=0.2,to=0.8,length=U)
params_start <- coef(b)
params_start[paste0("rho",1:U)] <- rho_start
ibpf_mle_searches <- foreach(reps=1:switch(i,3,10))%dopar%{
  ibpf(b,params=params_start,
    Nbpf=switch(i,2,50),Np=switch(i,10,1000),
    rw.sd=rw.sd(rho1=0.02,rho2=0.02,rho3=0.02,rho4=0.02),
    unitParNames="rho",
    sharedParNames=NULL,
    block_size=2,
    cooling.fraction.50=0.5
  )
}
@

@@

<<ibpf-prof,eval=T,echo=F>>=
stew(file=paste0(bm_dir,"prof1.rda"),seed=722,{
tic <- Sys.time()
u <- 1
rho_start <- seq(from=0.2,to=0.8,length=U)
reps <- switch(i,3,10)
param_start_matrix <- matrix(params_start,byrow=TRUE,
  ncol=length(coef(b)),nrow=reps*length(prof_vals),
  dimnames=list(NULL,names(coef(b))))
param_start_matrix[,paste0("rho",u)] <- rep(prof_vals,each=reps)
ibpf_prof_searches <- foreach(s=1:nrow(param_start_matrix))%dopar%{
  rw.sd_call <- rep(list(0.02),times=U-1)
  names(rw.sd_call) <- lapply((1:U)[-u],function(x)paste0("rho",x))
  ibpf(b,
    params=param_start_matrix[s,],
    Nbpf=switch(i,2,50),Np=switch(i,20,1000),
    rw.sd=do.call(rw.sd,rw.sd_call),
    unitParNames="rho",
    sharedParNames=NULL,
    block_size=2,
    cooling.fraction.50=0.5
  )
}
toc <- Sys.time()
})
prof1time <- toc-tic
@

@@

<<model-he10-plot,eval=T,echo=F,fig.height=7, fig.width=6, out.width="6.5in", fig.cap = "Weekly measles case reports. (A) Data for four UK towns. (B) Simulated data.">>=
m_dir <- paste0("m_",i,"/")
if(!dir.exists(m_dir)) dir.create(m_dir)
stew(file=paste0(m_dir,"m-sim.rda"),{
<<model-he10-code>>
})
library(grid)
library(cowplot)
plot_data <- plot(he10_model,log=T)+xlab("")
plot_sim <- plot(m,log=T)+xlab("Year")
plot_grid(
  plot_data,
  plot_sim,
  labels=c("A","B"),
  nrow=2,ncol=1
)
@

@@

<<m-prof-R0,eval=T,echo=F>>=
stew(file=paste0(m_dir,"m_prof_R02.rda"),seed=722,{
m_prof_R0_vals <- seq(from=25,to=35,length=switch(i,5,20))
tic <- Sys.time()
m_R0 <- m
m_R0_prof_u <- 1
reps <- switch(i,3,10)
param_R0_start_matrix <- matrix(coef(m_R0),byrow=TRUE,
  ncol=length(coef(m_R0)),nrow=reps*length(m_prof_R0_vals),
  dimnames=list(NULL,names(coef(m_R0))))
param_R0_start_matrix[,paste0("R0",m_R0_prof_u)] <- rep(m_prof_R0_vals,each=reps)
m_prof_R0_searches <- foreach(s=1:nrow(param_R0_start_matrix))%dopar%{
  rw.sd_call <- rep(list(0.02),times=U-1)
  names(rw.sd_call) <- lapply((1:U)[-m_R0_prof_u],function(x)paste0("R0",x))
  ibpf(m_R0,
    params=param_R0_start_matrix[s,],
    Nbpf=switch(i,2,50),Np=switch(i,10,2000),
    rw.sd=do.call(rw.sd,rw.sd_call),
    unitParNames="R0",
    sharedParNames=NULL,
    block_size=1,
    cooling.fraction.50=0.5
  )
}
toc <- Sys.time()
prof_R0_cores <- cores
})
m_prof_R0_time <- toc-tic
@

>>>>

<<bm_logLik_eval,cache=F,echo=F,eval=T>>=
bm_dir <- paste0("bm_",i,"/")
if(!dir.exists(bm_dir)) dir.create(bm_dir)
stew(file=paste0(bm_dir,"logLik.rda"),seed=10,{

  cat(capture.output(sessionInfo()),
    file=paste0(bm_dir,"sessionInfo.txt"),sep="\n")

<<bm_logLik_code>>
  bpf_logLik1 <- replicate(10,
    logLik(bpfilter(b,switch(i,10,1000),block_size=1))
  )
  bpf_logLik4 <- replicate(10,
    logLik(bpfilter(b,switch(i,10,1000),block_size=4))
  )
})
@

@@

<<ibpf-mle-code,eval=F,echo=T>>=
rho_start <- seq(from=0.2,to=0.8,length=U)
params_start <- coef(b)
params_start[paste0("rho",1:U)] <- rho_start
ibpf_mle_searches <- foreach(reps=1:switch(i,3,10))%dopar%{
  ibpf(b,params=params_start,
    Nbpf=switch(i,2,50),Np=switch(i,10,1000),
    rw.sd=rw_sd(rho1=0.02,rho2=0.02,rho3=0.02,rho4=0.02),
    unitParNames="rho",
    sharedParNames=NULL,
    block_size=2,
    cooling.fraction.50=0.5
  )
}
@

@@

<<ibpf-prof,eval=T,echo=F>>=
stew(file=paste0(bm_dir,"prof1.rda"),seed=722,{
  tic <- Sys.time()
  u <- 1
  rho_start <- seq(from=0.2,to=0.8,length=U)
  reps <- switch(i,3,10)
  param_start_matrix <- matrix(params_start,byrow=TRUE,
    ncol=length(coef(b)),nrow=reps*length(prof_vals),
    dimnames=list(NULL,names(coef(b))))
  param_start_matrix[,paste0("rho",u)] <- rep(prof_vals,each=reps)
  ibpf_prof_searches <- foreach(s=1:nrow(param_start_matrix))%dopar%{
    rw_sd_call <- rep(list(0.02),times=U-1)
    names(rw_sd_call) <- lapply((1:U)[-u],function(x)paste0("rho",x))
    ibpf(b,
      params=param_start_matrix[s,],
      Nbpf=switch(i,2,50),Np=switch(i,20,1000),
      rw.sd=do.call(rw_sd,rw_sd_call),
      unitParNames="rho",
      sharedParNames=NULL,
      block_size=2,
      cooling.fraction.50=0.5
    )
  }
  toc <- Sys.time()
})
prof1time <- toc-tic
@

@@

<<model-he10-plot,eval=T,echo=F,fig.height=7, fig.width=6, out.width="6.5in", fig.cap = "Weekly measles case reports. (A) Data for four UK towns. (B) Simulated data.">>=
m_dir <- paste0("m_",i,"/")
if(!dir.exists(m_dir)) dir.create(m_dir)
stew(file=paste0(m_dir,"m-sim.rda"),{
  cat(capture.output(sessionInfo()),
    file=paste0(m_dir,"sessionInfo.txt"),sep="\n")
<<model-he10-code>>
})
library(grid)
library(cowplot)
plot_data <- plot(he10_model,log=T)+xlab("")
plot_sim <- plot(m,log=T)+xlab("Year")
plot_grid(
  plot_data,
  plot_sim,
  labels=c("A","B"),
  nrow=2,ncol=1
)
@

@@

<<m-prof-R0,eval=T,echo=F>>=
stew(file=paste0(m_dir,"m_prof_R02.rda"),seed=722,{
m_prof_R0_vals <- seq(from=25,to=35,length=switch(i,5,20))
tic <- Sys.time()
m_R0 <- m
m_R0_prof_u <- 1
reps <- switch(i,3,10)
param_R0_start_matrix <- matrix(coef(m_R0),byrow=TRUE,
  ncol=length(coef(m_R0)),nrow=reps*length(m_prof_R0_vals),
  dimnames=list(NULL,names(coef(m_R0))))
param_R0_start_matrix[,paste0("R0",m_R0_prof_u)] <- rep(m_prof_R0_vals,each=reps)
m_prof_R0_searches <- foreach(s=1:nrow(param_R0_start_matrix))%dopar%{
  rw_sd_call <- rep(list(0.02),times=U-1)
  names(rw_sd_call) <- lapply((1:U)[-m_R0_prof_u],function(x)paste0("R0",x))
  ibpf(m_R0,
    params=param_R0_start_matrix[s,],
    Nbpf=switch(i,2,50),Np=switch(i,10,2000),
    rw.sd=do.call(rw_sd,rw_sd_call),
    unitParNames="R0",
    sharedParNames=NULL,
    block_size=1,
    cooling.fraction.50=0.5
  )
}
toc <- Sys.time()
prof_R0_cores <- cores
})
m_prof_R0_time <- toc-tic
@
